Four-body L=1 systems from contact EFT

### 2022-03-28 manuscript/Draft_0.3.tex
India V2 -- plots added to manuscript

\usepackage{graphicx} 
\usepackage{dashrule}
\usepackage{dcolumn} 
\usepackage{longtable} 
\usepackage{mathtools}
\usepackage{amssymb} 
\usepackage{bbold}
\usepackage{amsmath} 
\usepackage{amsfonts} 
\usepackage{wasysym}
\usepackage{slashed} 
\usepackage[dvipsnames]{xcolor} 
\usepackage{soul}
\usepackage{rotating}
\usepackage{paracol}
\usepackage{nicefrac}
\usepackage{MnSymbol}

@@

\newcommand{\eg}{\textit{e.g.}~}
\newcommand{\ie}{\textit{i.e.}~}
\newcommand{\viz}{\textit{viz.}~}
\newcommand{\cf}{\textit{cf.}~}
\newcommand{\eftnopi}{\mbox{EFT$(\not \! \pi)$}}
\newcommand{\ve}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\rcm}{\ensuremath{\ve{R}_\text{\scriptsize{c.m.}}}}
\newcommand*{\mprime}{^{\prime}\mkern-1.2mu}
\newcommand*{\mdprime}{^{\prime\prime}\mkern-1.2mu}
\newcommand*{\mtprime}{^{\prime\prime\prime}\mkern-1.2mu}
\newcommand{\ddrei}[1]{\delta_{\tiny \lambda}^{(3)}\!\big(#1\big)}
\newcommand{\cc}{\ensuremath C(\lambda)}
\newcommand{\dd}{\ensuremath D(\lambda)}

@@

\cf\eqref{eq.app.rgmwfkt}, first term. The parameter representation employed with the second equality in \eqref{eq.app.rgmwfkt2}
will yield a defining equation for the relative motion independent of the antisymmetrizer $\mathcal{A}$.
Assuming an inert triton core allows solely for a variation of the relative wave function:

@@

Employing the parameter representation, $\chi(\ve{R})=\int\delta(\ve{R}-\ve{R}\mprime)\chi{\ve{R}\mprime}d\ve{R}\mprime$,
and expanding the triton ground state in Gaussians,
$\phi(3)=\sum_n^{N_f}\,c_n\cdot e^{-\alpha_n\sum_{i=1}^{N_A}\left(\ve{r}_i-\ve{R}_3\right)^2}$,
in combination with the leading-order \eftnopi~potential

\begin{equation}\label{eq.app.pot}
\mathcal{V}_{31}=\cc\,\sum_{i\in A\atop j\in B}\,\ddrei{\ve{r}_i-\ve{r}_j}+
\dd\,\sum_{i,j,k\atop i\in A\Rightarrow j\vee k\in B}\ddrei{\ve{r}_i-\ve{r}_j}\,\ddrei{\ve{r}_i-\ve{r}_k}
\end{equation}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{./Graphs/rgm_potential} 
\caption{Two-fragment potential as a function of the distance between a
neutron and the center of mass of a triton. The plot shows the $P$-wave component of the
interaction including local and non-local part of the kinetic-, pair-, and three-body interactions.
The non-local parts are evaluated at $\rho=\rho'$}
\label{fig:rgm_potential}
\end{figure}

>>>>

\usepackage{graphicx} 
\usepackage{dashrule}
\usepackage{dcolumn} 
\usepackage{mathtools}
\usepackage{amssymb} 
\usepackage{bbold}
\usepackage{amsmath} 
\usepackage{amsfonts} 
\usepackage{wasysym}
\usepackage{slashed} 
\usepackage[dvipsnames]{xcolor} 
\usepackage{soul}
\usepackage{rotating}
\usepackage{paracol}
\usepackage{nicefrac}
\usepackage{MnSymbol}
\usepackage{caption}

@@

\newcommand{\figref}[1]{fig.~(\ref{#1})}
\newcommand{\tabref}[1]{table~(\ref{#1})}
\newcommand{\eref}[1]{eq.~(\ref{#1})}
\newcommand{\eg}{\textit{e.g.}~}
\newcommand{\ie}{\textit{i.e.}~}
\newcommand{\viz}{\textit{viz.}~}
\newcommand{\cf}{\textit{cf.}~}
\newcommand{\eftnopi}{\mbox{EFT($\slashed{\pi}$) }} 
\newcommand{\ve}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\rcm}{\ensuremath{\ve{R}_\text{\scriptsize{c.m.}}}}
\newcommand*{\mprime}{^{\prime}\mkern-1.2mu}
\newcommand*{\mdprime}{^{\prime\prime}\mkern-1.2mu}
\newcommand*{\mtprime}{^{\prime\prime\prime}\mkern-1.2mu}
\newcommand{\ddrei}[1]{\delta_{\tiny \lambda}^{(3)}\!\big(#1\big)}
\newcommand{\cc}{\ensuremath C(\lambda)}
\newcommand{\dd}{\ensuremath D(\lambda)}
\newcommand{\hbstwom}{\ensuremath \frac{\hbar^2}{2\mu}}
\newcommand{\twomhbs}{\ensuremath \frac{2\mu}{\hbar^2}}
\newcommand{\coup}[3]{\left[\,#1\,\otimes\,#2\,\right]^{#3}}
\newcommand{\threej}[6]{ \begin{pmatrix}
   #1 & #2 & #3 \\
   #4 & #5 & #6 
  \end{pmatrix}}

@@

\cf\eref{eq.app.rgmwfkt}, first term. The parameter representation employed with the second equality in \eref{eq.app.rgmwfkt2}
will yield a defining equation for the relative motion independent of the antisymmetrizer $\mathcal{A}$.
Assuming an inert triton core allows solely for a variation of the relative wave function:

@@

This expression is further evaluated by:
(i)~employing the parameter representation, $\chi(\ve{R})=\int\delta(\ve{R}-\ve{R}\mprime)\chi(\ve{R}\mprime)d\ve{R}\mprime$;
(ii)~expanding the triton ground state in Gaussians,
$\phi(3)=\sum_n^{N_f}\,c_n\cdot e^{-\alpha_n\sum_{i=1}^3\left(\ve{r}_i-\ve{R}_3\right)^2}$ with norm
$\mathbb{N}_3=\sum_{i,j=1}^{N_f}c_ic_j\left(\frac{\pi}{\alpha_i+\alpha_j}\right)^{\nicefrac{3}{2}}$;
(iii)~substituting the leading-order \eftnopi~potential as inter-cluster interaction,

\begin{eqnarray}\label{eq.app.pot}
\mathcal{V}_{31}
&=&
\cc\,\sum_{i\in A\atop j\in B}\,\ddrei{\ve{r}_i-\ve{r}_j}+
\dd\,\sum_{i,j,k\atop i\in A\Rightarrow j\vee k\in B}\ddrei{\ve{r}_i-\ve{r}_j}\,\ddrei{\ve{r}_i-\ve{r}_k}
\nonumber\\
&=&
\cc\cdot\left(\ddrei{\ve{r}_2-\ve{r}_4}+\ddrei{\ve{r}_3-\ve{r}_4}\right)
+\dd\cdot\left(\ddrei{\ve{r}_2-\ve{r}_3}\,\ddrei{\ve{r}_2-\ve{r}_4}\right)
\qquad;
\end{eqnarray}

(iv)~performing the action of $\mathcal{A}_{31}$ on $\phi_3$ and $\delta(\ve{R}-\ve{R}\mprime)$;
and finally, (v)~doing the Gaussian integrals for the triton-internal single-particle coordinates $\ve{r}_{1,2,3}$.
Thereby, one obtains the form

\begin{equation}\label{eq.app.rgmform}
(\hat{T}-E)~\chi(\ve{R})+\mathcal{V}^{(1)}(\ve{R})~\chi(\ve{R})+
\int d^{(3)}\ve{R}\mprime~\mathcal{V}^{(2)}(\ve{R},\ve{R}\mprime,E)~\chi(\ve{R}\mprime)=0
\qquad.
\end{equation}

More conveniently, we do express this equation as

\begin{gather}\label{eq.app.rgm.sglnonloc}
\mathbb{N}_3\cdot\left(-\ve{\Delta}_R-\ve{p}^2\right)\,\chi(\ve{R})+
\sum_{i,j=1}^{N_f}c_ic_j\left[
\sum_{n=1}^{2}\eta^{(ij)}_n~e^{-w^{(ij)}_n\ve{R}^2}\chi(\ve{R})-
\sum_{n=1}^{3}\int\left\lbrace\zeta^{(ij)}_n\hat{\zeta}_n\,e^{-a^{(ij)}_n\ve{R}^2-b^{(ij)}_n\ve{R}\cdot\ve{R}'-c^{(ij)}_n\ve{R}'^2}\right\rbrace\chi(\ve{R}') d\ve{R}'
\right]
=0
\\
\intertext{with $\hat{\eta}_n,\hat{\zeta}_n,w_n,a_n,b_n,c_n$ dependent upon,
(i) the low-energy constants: $\cc,\dd$, (ii) the triton-expansion parameters: $\alpha_n, c_n$,
(iii) the regulator parameter: $\lambda$, and (iv) the relative momentum: $\ve{p}^2=2\mu E$, as given in \tabref{tab.app.pot.coffs}.\nonumber} 
\end{gather}

\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.6}
\begin{table}
\begin{tabular}{l|c|c|c|c}
$n$ & $\eta^{(ij)}$  & $w^{(ij)}$ & & \\\hline
1   & $\frac{2\cc}{\left[2(\alpha_i+\alpha_j)(3\alpha_i+3\alpha_j+2\lambda)\right]^{\nicefrac{3}{2}}}$ & 
      $\frac{3(\alpha_i+\alpha_j)\lambda}{3(\alpha_i+\alpha_j)+2\lambda}$ &  &  \\
2   & $\frac{\dd}{\left[6(\alpha_i+\alpha_j)^2+16\lambda(\alpha_i+\alpha_j)+2\lambda^2\right]^{\nicefrac{3}{2}}}$ & 
      $\frac{3(\alpha_i+\alpha_j)\lambda((\alpha_i+\alpha_j)+2\lambda)}{3(\alpha_i+\alpha_j)^2+8(\alpha_i+\alpha_j)\lambda+\lambda^2}$ &  &  \\
\hline\hline
           & $\zeta^{(ij)}\otimes\hat{\zeta}$ & $a^{(ij)}$ & $b^{(ij)}$ & $c^{(ij)}$ \\\hline
1   & $\hbstwom\frac{3^3}{2^6}~\frac{1}{\left[2(\alpha_i+\alpha_j)\right]^{\nicefrac{3}{2}}}\otimes\left(-\ve{\Delta}_R-\ve{p}^2\right)$ &
      $\frac{3}{32}(\alpha_i+9\alpha_j)$ & 
      $\frac{9}{16}(\alpha_i+\alpha_j)$ & 
      $\frac{3}{32}(9\alpha_i+\alpha_j)$ \\
2   & $-\frac{3^3}{2^5}~\frac{\cc}{\left[2(\alpha_i+\alpha_j)+\lambda\right]^{\nicefrac{3}{2}}}\otimes\mathbb{1}$ & 
      $\frac{3(\alpha_i^2+9\alpha_j^2+10\alpha_i\alpha_j+\lambda(14\alpha_i+18\alpha_j))}{16(2(\alpha_i+\alpha_j)+\lambda)}$ & 
      $\frac{18(\alpha_i+\alpha_j)(\alpha_i+\alpha_j)+2\lambda}{16(2(\alpha_i+\alpha_j)+\lambda)}$ & 
      $\frac{3(9\alpha_i^2+\alpha_j^2+10\alpha_i\alpha_j+\lambda(6\alpha_i+2\alpha_j))}{16(2(\alpha_i+\alpha_j)+\lambda)}$  \\
3   & $-\frac{3^3}{2^6}~\frac{\dd}{\left[2(\alpha_i+\alpha_j)+5\lambda\right]^{\nicefrac{3}{2}}}\otimes\mathbb{1}$ & 
      $\frac{3(\alpha_i^2+9\alpha_j^2+10\alpha_i\alpha_j+\lambda(16\alpha_i+36\alpha_j)+27\lambda^2)}{16(2(\alpha_i+\alpha_j)+5\lambda)}$ & 
      $\frac{18((\alpha_i+\alpha_j)^2+4\lambda(\alpha_i+\alpha_j)+3\lambda^2)}{16(2(\alpha_i+\alpha_j)+5\lambda)}$ & 
      $\frac{3(9\alpha_i^2+\alpha_j^2+10\alpha_i\alpha_j+\lambda(24\alpha_i+4\alpha_j)+3\lambda^2)}{16(2(\alpha_i+\alpha_j)+5\lambda)}$  \\
\hline\hline
\end{tabular}
\caption{\small{Local ($\eta,w$) and non-local ($\zeta,a,b,c$) components of the resonating-group \eref{eq.app.rgm.sglnonloc}.}}
\label{tab.app.pot.coffs}
\end{table}

The character of the interaction is expected to depend strongly on the spatial symmetry of the wave function, and as
the parities of the triton core and the point neutron are positive, the overall parity is set by the relative motion
$\chi$. In order to investigate the parity dependence, we project into partial waves:
Expanding $\chi(\ve{R})=R^{-1}\sum_{lm}\phi_{lm}(R)Y_{lm}(\hat{\ve{R}})$
and projecting from the left with
$R\,\int d^2\hat{\ve{R}}~Y^*_{lm}(\hat{\ve{R}})$
before substituting
$$
e^{-b\ve{R}\cdot\ve{R}'}=4\pi\sum_{LM}i^Lj_L(ib RR')Y^*_{LM}(\hat{\ve{R}})Y_{LM}(\hat{\ve{R}}')\;\;;\;\;
\ve{R}\cdot\ve{R}'=-\sqrt{3}\coup{\ve{R}_p}{\ve{R}\mprime_{-p}}{00}=\frac{4\pi}{3}RR'\sum_p(-)^p\,Y_{1p}Y'_{1-p}
$$
and $\ve{r}_m=\sqrt{\frac{4\pi}{3}}rY_{1,m}(\hat{\ve{r}})$
yields
\begin{align}
0~=&
~\mathbb{N}_3\cdot\left(\partial^2_R-\frac{l(l+1)}{R^2}+\ve{p}^2\right)
\phi_{lm}(R)
-
\twomhbs\sum_{i,j=1}^{N_f}c_ic_j\Bigg(
\sum_{n=1}^2\eta^{(ij)}_n~e^{-w^{(ij)}_nR^2}\phi_{lm}(R)\nonumber\\
%
&-\int dR\mprime~\phi_{lm}(R\mprime)~(4\pi RR\mprime )~\Bigg[
%
~\zeta^{(ij)}_1 \cdot e^{-a^{(ij)}_1R^2-c^{(ij)}_1R'^2}\cdot\Bigg\lbrace
\left[-(4(a^{(ij)}_1)^2R^2+(b^{(ij)}_1)^2R\mprime^2-2a^{(ij)}_1)+\frac{l(l+1)}{R^2}-\frac{2\mu}{\hbar^2}E\right]
 i^l j_{l}(ib^{(ij)}_1 RR')\nonumber\\
%
&-(4a^{(ij)}_1b^{(ij)}_1)\cdot RR\mprime\cdot
\sum_Li^Lj_L(ib^{(ij)}_1 RR')~\hat{L}~\hat{l}~\threej{L}{1}{l}{0}{0}{0}^2~\triangle_{L1l}\Bigg\rbrace
%
+\sum_{n=2}^3\zeta^{(ij)}_n\,i^l j_l(ib_n RR')\cdot 
e^{-a^{(ij)}_nR^2-c^{(ij)}_nR'^2}~\Bigg]\Bigg)\label{eq.app.sglnonloc.pw.l.noloc}
\end{align}
with a 3-$j$ symbol $\neq0\Leftrightarrow L+1+l=$~even, and $\triangle_{j_1j_2j_3}\neq0\Leftrightarrow j_3=|j_1-j_2|,\ldots,j_1+j_2$.
From this equation, we obtain solutions for $S$- and $P$-waves on a discrete, equidistant coordinate grid:
$R,R\mprime\in\lbrace r_0,r_0+\epsilon,r_0+2\epsilon,\ldots,,\underbrace{r_0+N_\text{\tiny grid}\epsilon}_{=:r_{N_\text{\tiny grid}+1}}\rbrace$.
We chose a maximal grid dimension such that for $R(\mprime)=r_{N_\text{\tiny grid}+1}$ both local and non-local interactions
vanish. Thence, we solve \eref{eq.app.sglnonloc.pw.l.noloc} for the {\it principal-value} wave function ($\phi^{(P)}$)
with the boundary condition

\begin{eqnarray}\label{eq.app.principal.value.wfkt}
\phi_{l,p}^{(P)}(R)
&
\stackrel{R\to\infty}{\simeq}
&
\sin\left(pR-\frac{\pi l}{2}\right)
+
K_l
\cdot
\cos\left(pR-\frac{\pi l}{2}\right)\\
&
=
&
\lim_{pR\to\infty}\left[u_l(pR)\right]
+
\tan\delta_l
\cdot
\lim_{pR\to\infty}\left[v_l(pR)\right]
=
\left\lbrace
\begin{array}{ll}
l=0:& \sin\left(pR\right)-\tan\delta_l\cos\left(pR\right)\\
l=1:& \frac{\sin\left(pR\right)}{pR}-\cos\left(pR\right)-\tan\delta_l\left[\frac{\cos\left(pR\right)}{pR}+\sin\left(pR\right)\right]
\end{array}
\right.
\;\;.
\quad
\end{eqnarray}

For the Riccati-Bessel, $u_l(z)=zj_l(z)$, and the Riccati-Neumann Functions, $v_l(z)=zn_l(z)$, we use
\cite{}~as reference, where $j_l(n_l)$ is the proper spherical Bessel(Neumann) function. Note, the relation
between the Neumann and the spherical Bessel function of the second kind: $n_l(z)=(-)^ly_l(z)$.
Now, we obtain the phase shifts from

\begin{equation}\label{eq.app.phases}
\tan\delta_l=\frac{\phi_{l,p}^{(P)}(r_{N_\text{\tiny grid}+1})}{v_l(pr_{N_\text{\tiny grid}+1})}-
\frac{u_l(pr_{N_\text{\tiny grid}+1})}{v_l(pr_{N_\text{\tiny grid}+1})}
\qquad.
\end{equation}

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth]{./Graphs/rgm_potential} 
\caption{Two-fragment potential as a function of the distance between a
neutron and the center of mass of a triton. The plot shows the $P$-wave component of the
interaction including local and non-local part of the kinetic-, pair-, and three-body interactions.
The non-local parts are evaluated at $R=R'$. The height of the potential's barrier shrinks continuously from
the smallest cutoff (fat blue) to the largest (red), with intermediate values represented by green, dashed curves.}
\label{fig:rgm_potential}
\end{figure}

\begin{figure*}[th]
\captionsetup{width=.4\linewidth,justification=raggedright}
\begin{tabular}{cc}
\begin{minipage}[t]{0.45\linewidth}
 \includegraphics[width=\textwidth]{./Graphs/rgm_potential_MinMax}
 \caption{Locus of the valley (red, dashed) and the barrier (blue, solid) of the effective resonating-group
 interaction (\figref{fig:rgm_potential}) as a function of the regulator parameter $\lambda$.}
\label{fig:rgm_pot_minmax}
\end{minipage}
&
\begin{minipage}[t]{0.45\linewidth}
 \includegraphics[width=\textwidth]{./Graphs/rgm_potential_DeltaMinMax}
\caption{Regulator dependence of the difference between the first local maximum of the effective resonating-group potential
(\figref{fig:rgm_potential}) and its first local minimum.}
\label{fig:rgm_pot_valbardiff}
\end{minipage}
\end{tabular}
\end{figure*}
